MSAD_PCA_Walkthrough

### 2017-07-04 README.Rmd

## Examples
These are the examples shown in the help files for the mspTrain(), mspMonitor(), and mspWarning() functions.
```{r mspExamples}
normal_switch_xts <- mspProcessData(faults = "NOC", faultStartIndex = 8500)
# The state values are recorded in the first column.
n <- nrow(normal_switch_xts)
nTrainObs <- floor(0.4 * n)

# Calculate the training summary, but save five observations for monitoring.
trainResults_ls <- mspTrain(data = normal_switch_xts[1:(n - 5), -1],
                            labelVector = normal_switch_xts[1:(n - 5), 1],
                            trainObs = nTrainObs,
                            lagsIncluded = c(0, -1))

trainResults_ls

# While training, we included 1 lag (the default), so we will also lag the
# observations we will test.
testObs <- normal_switch_xts[(n - 6):n, -1]
testObs <- xts:::lag.xts(testObs, 0:1)
testObs <- testObs[-1,]
testObs <- cbind(normal_switch_xts[(n - 5):n, 1], testObs)
testObs

@@

dataAndFlags

>>>>

## Examples
These are the examples shown in the help files for the mspProcessData(), mspTrain(), mspMonitor(), and mspWarning() functions.
```{r mspExamples}
# Generate one week's worth of normal operating (NOC) data recorded at the one-
# minute level
noc_xts <- mspProcessData(faults = "NOC")
# The state values are recorded in the first column.
n <- nrow(noc_xts)

# Calculate the training summary, but save five observations for monitoring.
# This function will treat the first 3 days as in control (IC), and then update
# the training window each day.
trainResults_ls <- mspTrain(data = noc_xts[1:(n - 5), -1],
                            labelVector = noc_xts[1:(n - 5), 1],
                            trainObs = 4320)

# While training, we included 1 lag (the default), so we will also lag the
# observations we will test.
testObs <- noc_xts[(n - 6):n, -1]
testObs <- xts:::lag.xts(testObs, 0:1)
testObs <- testObs[-1,]
testObs <- cbind(noc_xts[(n - 5):n, 1], testObs)

@@
